%% Copyright 2013 BarD Software s.r.o
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

% \documentclass[11pt,a4paper]{moderncv}
% \moderncvtheme[grey]{classic}
% \usepackage[utf8]{inputenc}
% \usepackage[T2A]{fontenc}
% \usepackage[english,russian]{babel}
\documentclass[11pt,a4paper]{moderncv-xetex}
\moderncvtheme[grey]{papeeria}

\usepackage{xcolor}
\newfontfamily{\cyrillicfonttt}{CMU Typewriter Text}
\usepackage[a4paper,margin=1in]{geometry}

\firstname{Gregory}\familyname{Kalabin}
\mobile{+44-7949-273-728}
%\phone{}
\email{gregory@kalabin.net}
\address{London, UK}{}{}
\quote{
    \url{linkedin.com/in/gkalabin/}\\
    \url{github.com/gkalabin}
}

%\nopagenumbers{}

\begin{document}
\setlength{\parskip}{2em}
\maketitle

Software Engineering Leader with 15 years of experience spanning IC and management roles at Google, Booking.com, and startups. Proven track record of scaling high-throughput backend systems (1M+ QPS), leading reliability projects for global cloud infrastructure (GCE), and building high-performing engineering teams. Deep expertise in Golang, Java, Kubernetes, and distributed systems.

\cventry{Since April 2025}{Google}{Software Engineering Manager}{Google Compute Engine}{}
{
• Defined and executed multi-year engineering roadmap for GCE Control Plane Reliability to uphold 99.95\% global availability target.
\\
• Built a high performing team of 7 Software Engineers: hired talent and supported career development that resulted in 2 successful promotions.
\\
• Led a cross-organizational infrastructure initiative, unlocking deployments for 20+ engineering teams and enabling the organic growth of 50+ services.
\\
• Built infrastructure to enforce best reliability practices across 50+ services to enable the services handle 1M+ QPS.
\\
• Maintaining hands-on IC contributions, adopting new tools and staying in touch with what people on the team are experiencing.
\\
• Member of oncall rotation responsible for the reliability of the GCE API defending 99.95\% availability globally. Incident Commander of 2 global outages.
}

\cventry{October 2020 to April 2025}{Google}{Senior Software Engineer in Site Reliability}{Google Compute Engine}{}
{
• Tech Lead of an SRE team, owned the team roadmap and execution together with the manager.
\\
• Landed multi-year projects involving 4 separate developer organisations. Designed and developed new services in the GCE Control Plane and worked across the organisation to unblock GCE API traffic migration.
\\
• Developed a capacity management tool utilized across Google, preventing 10+ major outages by surfacing relevant capacity changes to the teams.
\\
• Incident Commander of major outages: mitigated impact, involved and coordinated with Google infrastructure teams during the incident, wrote postmortem and made sure the followups were addressed.
\\
• Coached and mentored other Software Engineers.
}


\cventry{April 2018 to July 2020}{Booking.com}{Software Engineering Manager}{}{}
{
Held a combined role of Software Engineering Manager and Senior Software Developer: directly managed a team of Software Engineers alongside delivering hands on work.
\\
\\
 • Managed a team of software engineers. Provided mentoring and coaching for the team members, owned multiple successful promotions and hired talent.
\\
 • Designed and executed multi-quarter team roadmap. Partnered with the stakeholders and platform customers.
\\
 • Scaled the experimentation platform to microservices. Launched the first A/B tests in Java and JavaScript. Onboarded the biggest Java service onto the A/B testing platform.
\\
 • Integrated A/B testing platform into Booking.com's Kubernetes infrastructure. Built and owned a sidecar running alongside every service in the company.
\\
 • Built highly scalable system which handled 400k+ requests per second.
\\
 • Designed, wrote and maintained client libraries for Java, JavaScript and Perl.
}


\cventry{March 2017 to April 2018}{Booking.com}{Full Stack Software Developer}{}{}
{
Full Stack Software Developer on Partner Experiments Team responsible for A/B testing platform for Booking.com partners:
\\
 • Extended the existing A/B testing platform to Booking.com partners.
\\
 • Collaborated with data scientists on building trustworthy metrics for analysing changes in partner behaviour.
\\
 • Enabled customer support metrics for A/B tests for all of the product teams.
\\
 • Maintained data pipelines generating metrics and minimising the data loss.
\\
 • Partnered with product management and data science teams to develop the A/B testing platform.
}
    
\cventry{July 2015 to March 2017}{Lazada}{Senior Software Developer}{}{}
{
Senior Golang Software Developer.
\\
 • Developed a highly performant frontend Golang server, reducing page latency to sub-50ms.
\\
 • Profiled and debugged performance bottlenecks in Golang applications.
\\
 • Designed and implemented config distribution library.
}
    
\cventry{November 2012 to July 2015}{Papeeria.com}{Full Stack Developer}{}{}
{Full Stack Developer in a 3-person startup changing the way people write scientific papers.}

\cventry{June 2011 to November 2012}{Lanit-Tercom}{Junior Software Engineer}{}{}
{Android developer, contributor to two major android apps the company was developing for external clients.
}


\section{Technologies}
\cvline{Skills}{Technical Leadership, Distributed Systems, Kubernetes}
\cvline{Languages}{Java, Go, Python, Typescript/Javascript, Perl}


\section{Education}
\cvline{2008\,--\,2013}{Specialist (Master's equivalent)
\newline
\small{Saint-Petersburg State University, Applied Mathematics}
}

\end{document}
