%% Copyright 2013 BarD Software s.r.o
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

% \documentclass[11pt,a4paper]{moderncv}
% \moderncvtheme[grey]{classic}
% \usepackage[utf8]{inputenc}
% \usepackage[T2A]{fontenc}
% \usepackage[english,russian]{babel}
\documentclass[11pt,a4paper]{moderncv-xetex}
\moderncvtheme[grey]{papeeria}

\usepackage{xcolor}
\newfontfamily{\cyrillicfonttt}{CMU Typewriter Text}
\usepackage[a4paper,margin=1in]{geometry}

\firstname{Gregory}\familyname{Kalabin}
\mobile{+44-7949-273-728}
%\phone{}
\email{gregory@kalabin.net}
%\extrainfo{}
\quote{Software Engineering Leader with 15+ years of experience}

%\nopagenumbers{}

\begin{document}
\maketitle

\cventry{Since April 2025}{Google}{Software Engineering Manager}{}{}
{• Manager of Software Engineering team in Site Reliability of Google Compute Engine.
\\
• Owning the team charter, roadmap and execution. Close partnership with the stakeholders to align on the progress and proactively address risks.
\\
• Performance management of Software Engineers. Ran multiple successful promotion cases for my team.
\\
• Execution owner of critical cross organisation projects. As a result, supported organic growth of 50+ services owned by dozens of teams.
\\
• Hands on Software Development on the team.
\\
• Member of oncall rotation defending whole of the GCE API reliability.
\\
• Coached and mentored Software Engineers in my team and beyond.
}

\cventry{October 2020 to April 2025}{Google}{Senior Software Engineer in Site Reliability}{}{}
{
• Software Engineer in Site Reliability of Google Compute Engine.
\\
• Tech Lead of an SRE team, owned the roadmap and execution in the team in partnership with the manager of the team.
\\
• Landed projects spanning a number of developer organisations: designed new services in the GCE Control Plane and worked across the organisation to enable migration of all of the GCE API traffic to them. Resolved conflicts and aligned on common solutions.
\\
• Improved capacity management of the GCE Control Plane, developed tools used across all of Google to safely adjust deployment size.
\\
• Led multiple major outages as the Incident Commander to resolution: mitigated impact, debugged the problem, wrote postmortem and worked with the stakeholders to address discovered reliability gaps.
\\
• Coached and mentored other Software Engineers.
}


\cventry{April 2018 to July 2020}{Booking.com}{Software Engineering Manager}{}{}
{
Held a combined role of Software Engineering Manager and Senior Software Developer in which I directly managed a team of Software Engineers alongside delivering hands on work on the team.
\\
\\
As a people manager:
\\
 • Managed a team of software engineers.
\\
 • Provided mentoring and coaching for the team members to help succeed in their career.
\\
 • Did performance management: prepared and participated in the calibration sessions and delivered perf results.
\\
 • Hired talent for the team
\\
\\
As a tech lead and a senior software engineer:
\\
 • Designed and owned the execution of the team roadmap. Collected requirements from the stakeholders. Supported team members in the execution of the roadmap and resolving blockers they had.
\\
 • Expanding existing experimentation platform to support microservices. We launched the first A/B test in Java and JavaScript and onboarded the biggest Java service (HotelPage API) on A/B testing platform.
\\
 • Building highly scalable system which handled 400k+ requests per second.
\\
 • Designing, writing and maintaining client libraries for Java, JavaScript and Perl.
\\
 • Partnered with Product Managers to align the product and technical roadmaps.
}


\cventry{March 2017 to April 2018}{Booking.com}{Full Stack Software Developer}{}{}
{
Full Stack Software Developer on Partner Experiments Team responsible for A/B testing platform for Booking.com partners (e.g. hotels or property managers):
\\
 • Extending the existing A/B testing platform to Booking.com partners.
\\
 • Collaboration with data scientists on building trustworthy metrics for analysing changes in partner behaviour.
\\
 • Enabling customer support metrics for A/B tests for all of the product teams.
\\
 • Maintaining data pipelines generating metrics and minimising the data loss.
\\
 • Partnering with product management and data science teams to develop the A/B testing platform.
}
    
\cventry{July 2015 to March 2017}{Lazada}{Senior Software Developer}{}{}
{
Senior Software Developer developing microservices in Golang.
\\
 • Developing frontend server in Golang serving pages within 50ms and handling 100+ QPS.
\\
 • Profiling and debugging performance bottlenecks in golang applications.
\\
 • Designing and implementing config distribution library.
}
    
\cventry{November 2012 to July 2015}{Papeeria.com}{Full Stack Developer}{}{}
{Full Stack Developer in a 3-people startup for changing the way people write scientific papers.}

\cventry{June 2011 to November 2012}{Lanit-Tercom}{Junior Software Engineer}{}{}
{Android developer, contributor to two major android apps the company was developing for external clients.
}


% ТЕХНИЧЕСКИЕ НАВЫКИ -------------------------------------------------
\section{Technologies}
\cvline{Languages}{Russian, English, Java, Go, Perl, Javascript, Bash, Scala, Python}

% ОБРАЗОВАНИЕ --------------------------------------------------------
\section{Education}
\cvline{2008\,--\,2013}{Five-year degree (Level 7 in ISCED classification of UNESCO 2011)
\newline
\small{Saint-Petersburg State University, Mathematics and Mechanics faculty}
}

\end{document}
