\documentclass[11pt,a4paper]{moderncv-xetex}
\moderncvtheme[grey]{papeeria}
\usepackage{xcolor}
\newfontfamily{\cyrillicfonttt}{CMU Typewriter Text}
\usepackage[a4paper,margin=1in]{geometry}

\firstname{Gregory}\familyname{Kalabin}
\mobile{+44-7949-273-728}
\email{gregory@kalabin.net}
\address{London, UK}{}{}
\quote{
    \url{linkedin.com/in/gkalabin/}\\
    \url{github.com/gkalabin}
}

\begin{document}
\setlength{\parskip}{2em}
\maketitle

Software Engineering Leader with 15 years of experience spanning IC and management roles at Google, Booking.com, and startups. Proven track record of scaling high-throughput backend systems (1M+ QPS), leading reliability projects for global cloud infrastructure (GCE), and building high-performing engineering teams. Deep expertise in Golang, Java, Kubernetes, and distributed systems.

\cventry{Since April 2025}{Google}{Software Engineering Manager}{Google Compute Engine}{}
{
• Defined and executed a multi-year engineering roadmap for GCE Control Plane Reliability to uphold the 99.95\% availability target.
\\
• Built a high-performing team of 7 Software Engineers: hired talent and supported career development, resulting in 2 successful promotions.
\\
• Led a cross-organizational infrastructure initiative, unlocking deployments for 20+ engineering teams and enabling the organic growth of 50+ services.
\\
• Built infrastructure to enforce best reliability practices across 50+ services, enabling the services to handle 1M+ QPS.
\\
• Maintained hands-on IC contributions, adopting new tools and staying in touch with what team members are experiencing.
\\
• Served as a member of the on-call rotation responsible for the reliability of the GCE API, defending 99.95\% availability globally.
}

\cventry{October 2020 to April 2025}{Google}{Senior Software Engineer in Site Reliability}{Google Compute Engine}{}
{
• Served as Tech Lead of an SRE team; owned the team roadmap and execution in partnership with the manager.
\\
• Delivered multi-year project involving 4 separate developer organisations. Designed and developed new services in the GCE Control Plane and worked across the organisation to unblock the GCE API traffic migration.
\\
• Developed a capacity management tool utilised across Google, preventing at least 3 major outages by surfacing relevant capacity changes to service owners.
\\
• Served as Incident Commander for 2 major outages: mitigated impact, coordinated with Google infrastructure teams during incidents, wrote postmortems, and ensured follow-ups were addressed.
\\
• Coached and mentored other Software Engineers.
}


\cventry{April 2018 to July 2020}{Booking.com}{Software Engineering Manager}{}{}
{
Held a combined role of Software Engineering Manager and Senior Software Developer: directly managed a team of Software Engineers alongside delivering hands-on work.
\\
\\
• Managed a team of software engineers. Provided mentoring and coaching for team members, owned multiple successful promotions, and hired talent.
\\
• Designed and executed a multi-quarter team roadmap. Partnered with stakeholders and platform customers.
\\
• Scaled the experimentation platform to microservices. Launched the first A/B tests in Java and JavaScript. Onboarded the largest Java service onto the A/B testing platform.
\\
• Integrated the A/B testing platform into Booking.com's Kubernetes infrastructure. Built and owned a sidecar running alongside every service in the company.
\\
• Built a highly scalable system that handled 400k+ requests per second.
\\
• Designed, wrote, and maintained client libraries for Java, JavaScript, and Perl.
}


\cventry{March 2017 to April 2018}{Booking.com}{Full Stack Software Developer}{}{}
{
Full Stack Software Developer on the Partner Experiments Team, responsible for the A/B testing platform for Booking.com partners:
\\
• Extended the existing A/B testing platform to Booking.com partners.
\\
• Collaborated with data scientists on building trustworthy metrics for analysing changes in partner behaviour.
\\
• Enabled customer support metrics for A/B tests across all product teams.
\\
• Maintained data pipelines generating metrics and minimising data loss.
\\
• Partnered with product management and data science teams to develop the A/B testing platform.
}
    
\cventry{July 2015 to March 2017}{Lazada}{Senior Software Developer}{}{}
{
Senior Golang Software Developer.
\\
• Developed a highly performant frontend Golang server, reducing page latency to sub-50ms.
\\
• Profiled and debugged performance bottlenecks in Golang applications.
\\
• Designed and implemented a config distribution library.
}
    
\cventry{November 2012 to July 2015}{Papeeria.com}{Full Stack Developer}{}{}
{Full Stack Developer in a 3-person startup changing the way people write scientific papers.}

\cventry{June 2011 to November 2012}{Lanit-Tercom}{Junior Software Engineer}{}{}
{Android developer and contributor to two major Android apps the company was developing for external clients.
}


\section{Technologies}
\cvline{Skills}{Technical Leadership, Distributed Systems, Kubernetes}
\cvline{Languages}{Java, Go, Python, TypeScript/JavaScript}


\section{Education}
\cvline{2008\,--\,2013}{Specialist (Master's equivalent)
\newline
\small{Saint-Petersburg State University, Applied Mathematics}
}

\end{document}